### 2012-12-13 doc/description.tex
text about operations, cleaned definitions

\subsection{Application Evolution}
\label{sec:appEvolution}
\subsubsection{Application Creation}
$$AddClass: Class \times Application \rightarrow Application $$

$
AddClass(c, a) = \inference{\forall s \in classes(A) : name(s) \neq name(c)}
{application(classes(a) \cup c, instances(a))}
$

@@

$
AddProperty(l, p, a) = \inference{\exists c \in classes(a) : name(c) = l \\ \wedge \not \exist q \in properties(p) : name(q) \neq name(p)}{
application(classes(a)) \wedge properties(c) \cup p }
$

\subsubsection{Application Deconstruction}
$$RemoveClass: Label \times Application \rightarrow Application $$
$
RemoveClass(q, a) = \inference{\exists c \in classes(a) : name(c) = q \\
\wedge not$ $instantiated(c) = \{ \} \wedge not$ $associated(c)}{applicattion(classes(a) \setminus c, instances(a)) }
$

@@

$
RemoveProperty(l_c, l_p, a) = \inference{\exists c \in classes(a) : name(c) = l_c \\ \wedge \exists p \in properties(c) : name(p) = l_p}{}
$

@@

$
\rho : Property, Database \rightarrow Column 
$

@@

$
\rho_{addClass}(c, d) = \inference{\forall t \in tables(d) : name(t) \neq name(\rho(c)) \\
	\forall a \in \rho(associations(c)) : reference(a) \in tables(d) 
}{ %TODO podmínky?
\begin{gathered}
database(tables(d) \cup \rho(c) \cup \rho(properties(c)) \\ \cup \rho(associations(c)), instances(d))
\end{gathered}
}
$
\subsubsection{Add Property}
$
\rho_{addProperty}(l, p, d) =  \begin{cases}
\inference{\exists t \in tables(d) : name(t) = l \\ \wedge (cardinality(p) = 0 \vee cardinality(p) = 1)}{database(tables(d) \wedge columns(t) \cup \rho(p), instances(d))} 
\\ \\
\inference{\exists t \in tables(d) : name(t) = l \\ \wedge cardinality(p) > 1}{database(tables(d) \cup \rho(p), instances(d))}  
  \end{cases}
$

\subsection{Deconstruction of a System}
\subsubsection{Remove Class}
$
\rho_{removeClass}(c,d) = \inference{\rho(c) \in tables(d) \\ \wedge \not \exists r \in data(d) : owningTable(r) \neq \rho(c) \\ \not \exists j \in tables(d), f \in foreignKeys(j) : reference(f) = \rho(c)  }{tables(d) \setminus \rho(c)}
$

\subsubsection{Remove Property}

>>>>

\subsection{Application Evolution}
\label{sec:appEvolution}

The evolution is defined as a set of operations which change structure of an application. The definition of an operation consists of two parts - a conditions of operation feasibility and operation impact on the application structure. We decide to use following transcription:

$$
operation = \inference{conditions$ $of$ $feasibility}{impact$ $on$ $application$ $structure}
$$
If the conditions of feasibility are not met, the operation cannot impact the application structure.
%TODO monade

\subsubsection{Application Creation}
$$AddClass: Class \times Application \rightarrow Application $$

$
AddClass(c, a) = \inference{\forall s \in classes(A) : name(s) \neq name(c)}
{classes(a) \cup c}
$

@@

$
AddProperty(l, p, a) = \inference{\exists c \in classes(a) : name(c) = l \\ \wedge \not \exist q \in properties(p) : name(q) \neq name(p)}{
 properties(c) \cup p }
$

\subsubsection{Application Deconstruction}
$$RemoveClass: Label \times Application \rightarrow Application $$
$
RemoveClass(q, a) = \inference{\exists c \in classes(a) : name(c) = q \\
\wedge not$ $instantiated(c) = \{ \} \wedge not$ $associated(c)}{classes(a) \setminus c }
$

@@

$
RemoveProperty(l_c, l_p, a) = \inference{\exists c \in classes(a) : name(c) = l_c \\ \wedge \exists p \in properties(c) : name(p) = l_p}{properties(c) \setminus p }
$

@@

$
\rho : Property \times Database \rightarrow Column 
$

@@

$
\rho_{addClass}(c, d) = \inference{\forall t \in tables(d) : name(t) \neq name(\rho(c)) \\
	\forall a \in \rho(associations(c)) : reference(a) \in tables(d) 
}{ %TODO podmínky?
\begin{gathered}
tables(d) \cup \rho(c) \cup \rho(properties(c)) \cup \rho(associations(c))
\end{gathered}
}
$
\subsubsection{Add Property}
$
\rho_{addProperty}(l, p, d) = 
\inference{\exists t \in tables(d) : name(t) = l}{\rho(p,d)}

$

\subsection{Deconstruction of a System}
\subsubsection{Remove Class}
$
\rho_{removeClass}(c,d) = \inference{\rho(c) \in tables(d) \\ \wedge \not \exists r \in data(d) : owningTable(r) \neq \rho(c) \\ \not \exists j \in tables(d), f \in foreignKeys(j) : reference(f) = \rho(c)  }{tables(d) \setminus \rho(c)}
$
%TODO remove by label

\subsubsection{Remove Property}
$
\rho_{removeProperty}(l_c, l_p, d) = \inference{\exists t \in tables(d) : name(t) = l_c \\ \wedge \exists c \in columns(t) : name(c) = l_p }{
columns(t) \setminus c
}
$
